The language of generalization: Probability, vagueness, and interaction

### 2018-03-01 paper/comgen-paper.Rmd
address em comment about acquisition problem

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., probability $h$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data.

>>>>

Rejecting the tools of truth-functional semantics for generalizations would be throwing the baby out with the bathwater.
The acquisition of a threshold-based truth-functional meaning $\denote{u}(h, \theta) = \{h :h > \theta\}$ requires learning at least three distinct aspects of meaning: 
(1) the *dimension* being described (i.e., probability $h$),
(2) the *polarity* of the relation (i.e., $>$ vs. $<$), and 
(3) the value of the threshold (e.g., $\theta = 0$ for "some", $\theta = 0.5$ for "most").
Upon acquiring the dimension and the polarity, a rational learner should represent uncertainty over possible thresholds $\theta$.
Upon repeated cross-situational data, this prior could be updated towards acquiring a fixed meaning.
However, for generalizations, no fixed threshold is required; the language of generalization is learned once aspects (1) and (2) are understood.
Thus, under our framework, generalizations should not only be learned before, but also faciliate in learning, quantifiers.
<!-- In our model, $\theta$ is left underspecified in the semantics and is inferred in context. -->
<!-- This informal analysis predicts that a child would first acquire the language of generalizations, and from that, carve out more precise meanings for quantified language, consistent with the developmental data. -->
